---
title: "Tutorial reproducibility"
author: 
  - "Lars Vilhuber"
date: February 2025
---

```{r config,include=FALSE}
library(readr)
library(here)
library(knitr)
library(dplyr)
library(ggplot2)
library(qualtRics)
library(lubridate)

# qualtRics secrets are read from the environment:
# - QUALTRICS_API_KEY
# - QUALTRICS_BASE_URL
# Let's check that they are there:

message(Sys.getenv("QUALTRICS_BASE_URL"))


# Qualtrics data for Day 1:
# you can find this with all_surveys() %>% arrange(creationDate) %>% head()

QUALTRICS_FULL_URL <- "https://cornell.yul1.qualtrics.com/jfe/form"

# Public Qualtrics URL for day 2

QUALTRICS_DAY2 <- "SV_cNkhKL69K2Ob7o2"

# Time when this was posted (discard anything before that)

QUALTRICS_DAY2_STIME <- ymd_hms("2025-01-21 23:59:00")
QUALTRICS_DAY2_ETIME <- ymd_hms("2025-02-14 23:59:00")

if (!dir.exists(here::here("data"))) {
  dir.create(here::here("data"))
}
```

::: {.panel-tabset}


## Day 1

One of the following (or a linear combination):

- [Setting yourself up for reproducibility](https://larsvilhuber.github.io/day1-tutorial/)
- [How to correctly document a replication package](https://larsvilhuber.github.io/readme-presentation/)



## Survey 2

To identify what we should be speaking about on Day 2, please fill out this other survey:

<`r file.path(QUALTRICS_FULL_URL,QUALTRICS_DAY2)`>

### Results

```{r downloaddata2,include=FALSE}
# download data to local location

data2.raw <- fetch_survey(surveyID = QUALTRICS_DAY2, verbose = TRUE) 
data2 <- data2.raw |>
        filter(Status != "Survey Preview") |>
        filter(Consent == "I agree that my data will be used in the manner described.") |>
        #filter(StartDate > QUALTRICS_DAY2_STIME) |>
  # renaming variables
  select(StartDate,EndDate,Status,Finished,RecordedDate,ResponseId,Consent,Preferred_topic,Degree,JEL_primary,
         starts_with("JEL_secondary"),starts_with("Versioning_"))


```

```{r create_table2, results='asis', include=TRUE,echo=FALSE,message=FALSE}

if ( nrow(data2) >0 ) {
data2 |>
  select(Preferred_topic) |>
  group_by(Preferred_topic) |>
  summarise(Frequency=n()) |>
  ungroup() |>
  mutate(Percent = round(Frequency/nrow(data2)*100,2)) -> data2.table

data2.table |> kable()
} else {
  cat("No data yet. Check back later.")
}
```



## Day 2

One of the following (or a linear combination):

- [Reproducibility when some data are confidential](https://labordynamicsinstitute.github.io/reproducibility-confidential/) 
- [Advanced self-checking of reproducibility](https://larsvilhuber.github.io/self-checking-reproducibility/presentation/)


## Day 3


- JIT Preservation of research output

  - <https://labordynamicsinstitute.github.io/replication-tutorial-2019/#/18>
  - <https://labordynamicsinstitute.github.io/tutorial-data-sharing-archiving-2021/#/2> (possibly challenging)

- Short presentation on concerns about ethics in data dissemination
- **In-depth tutorial on the use of Docker for economics research**
  - <https://codeocean.com>
  - <https://github.com/codespaces>

```{r, child=c(here::here('99-links.md'))}
```

:::

